Debugging of RxJS-based Applications

### 2020-10-15 abstract.tex
Review Stef
Add ACM References

RxJS is a popular library to implement data-flow-oriented applications with JavaScript using reactive programming principles. This way of programming bears new challenges for traditional debuggers: Their focus on imperative programming limits their applicability to problems originated in the declarative programming paradigm. The goals of this paper are: (i) to understand how software engineers debug RxJS-based applications, what tools do they use, what techniques they apply; (ii) to understand what are the most prevalent challenges they face while doing so; and (iii) to provide a course of action to resolve these challenges in a future iteration on the topic. We learned about the debugging habits of ten professionals using interviews, and hands-on war story reports. Based on this data, we designed and executed an observational study with four subjects to verify that engineers predominantly augment source code with manuel trace logs instead of using specialized debugging utilities. In the end, we identified the lack of fully integrated RxJS-specific debugging solutions in existing development environments as the most significant reason why engineers do not make use of such tools. We decided to elaborate on how to resolve this situation in detail as the topic for our future work.

>>>>

RxJS is a popular library to implement data-flow-oriented applications with JavaScript using reactive programming principles. This way of programming bears new challenges for traditional debuggers: Their focus on imperative programming limits their applicability to problems originated in the declarative programming paradigm. The goals of this paper are: (i) to understand how software engineers debug RxJS-based applications, what tools do they use, what techniques they apply; (ii) to understand what are the most prevalent challenges they face while doing so; and (iii) to provide a course of action to resolve these challenges in a future iteration on the topic. We learned about the debugging habits of ten professionals using interviews, and hands-on war story reports. Based on this data, we designed and executed an observational study with four subjects to verify that engineers predominantly augment source code with manual trace logs instead of using specialized debugging utilities. In the end, we identified the lack of fully integrated RxJS-specific debugging solutions in existing development environments as the most significant reason why engineers do not make use of such tools. We decided to elaborate on how to resolve this situation in our future work.

### 2020-10-15 paper.tex
Add ACM References

\documentclass[sigplan,screen,review]{acmart}
% Class options:
%  - review: Show line numbers for reviewers
%  - nonacm: Hide ACM conference stuff

@@

% Top Matter: https://mirror.kumi.systems/ctan/macros/latex/contrib/acmart/acmart.pdf
\acmConference[SPLASH '20]{SPLASH 2020: 7th Workshop on Reactive and Event-based Languages \& Systems}{November 15--20, 2020}{Chicago}
\title{Debugging of RxJS-based Applications}
\author{Manuel Alabor}
\affiliation{
	\institution{Eastern Switzerland University of Applied Sciences}
	\city{Rapperswil}
	\country{Switzerland}
}
\email{manuel.alabor@ost.ch}

>>>>

\documentclass[sigplan,screen]{acmart}
% Class options:
%  - review: Show line numbers for reviewers
%  - nonacm: Hide ACM conference stuff

@@

%%% The following is specific to REBLS '20 and the paper
%%% 'Debugging RxJS-Based Applications'
%%% by Manuel Alabor.
%%%
\setcopyright{acmlicensed}
\acmPrice{15.00}
\acmDOI{10.1145/3427763.3428313}
\acmYear{2020}
\copyrightyear{2020}
\acmSubmissionID{splashws20reblsmain-p3-p}
\acmISBN{978-1-4503-8188-8/20/11}
\acmConference[REBLS '20]{Proceedings of the 7th ACM SIGPLAN International Workshop on Reactive and Event-Based Languages and Systems}{November 16, 2020}{Virtual, USA}
\acmBooktitle{Proceedings of the 7th ACM SIGPLAN International Workshop on Reactive and Event-Based Languages and Systems (REBLS '20), November 16, 2020, Virtual, USA}

% Top Matter: https://mirror.kumi.systems/ctan/macros/latex/contrib/acmart/acmart.pdf
\title{Debugging of RxJS-based Applications}
\author{Manuel Alabor}
\affiliation{
	\institution{Eastern Switzerland University of Applied Sciences}
	\city{Rapperswil}
	\country{Switzerland}
}
\email{manuel.alabor@ost.ch}
